%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerlastnamestyle{Charles Henry Armentrout V} \\
	\vspace{2mm}
	{\faEnvelope\ charlie@armentrout.dev} | {\faMobile\ 3366817224} | {\faMapMarker\ Raleigh, NC}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Professional Experience}
\begin{cventries}
	\cventry
	{Senior Engineer}
	{SignalPath / Verily}
	{Raleigh, NC}
	{Feb 2021 – Present}
	{\begin{cvitems}
		\item {Authored multiple architecture solutions for a greenfield financial ledger service to replace a legacy system and provide significant performance increases and new features.}
		\item {Performed interviews and mentored junior developers as they got up to speed on our technologies and systems}
		\item {Worked as part of an on-call team to rapidly respond to production issues if needed}
		\item {Scala, SQL, Slick, Finatra, Doobie}
		\end{cvitems}}
	\cventry
	{Lead Engineer}
	{The McClatchy Company}
	{Raleigh, NC}
	{Feb 2020 – Jan 2021}
	{\begin{cvitems}
		\item {Lead a team of remote engineers to update and modernize an ETL system for serverless architecture.}
		\item {Helped lead company technical strategy toward a less human resource intensive solution}
		\item {Cut infrastructure costs significantly by redesigning serverless strategy}
		\item {Python, S3, Lambda, Glue, SQS}
		\end{cvitems}}
	\cventry
	{Automation Architect}
	{Credit Suisse (Contract)}
	{Durham, NC}
	{Nov 2019 – Feb 2020}
	{\begin{cvitems}
		\item {Contracted to design an automation solution for security response workflows}
		\item {Python, Flask}
		\end{cvitems}}
	\cventry
	{Software Engineer / Senior Engineer}
	{Cisco Systems}
	{Durham, NC}
	{Jan 2017 – Nov 2019}
	{\begin{cvitems}
		\item {Engineer backend systems for network test automation application}
		\item {Design and implement system for performing network tests remotely}
		\item {Design and maintain application API through multiple versions and changes}
		\item {Python, Flask, Robot, TextFSM, Docker, K8S}
		\end{cvitems}}
	\cventry
	{Software Engineer}
	{Deloitte}
	{Morrisville, NC}
	{Jun 2014 – Jan 2017}
	{\begin{cvitems}
		\item {Maintained legacy python systems}
		\item {Refactored legacy systems into a microservice architecture}
		\item {Built tooling for service discovery and communication}
		\item {Python, SQL, Flask}
		\end{cvitems}}
\end{cventries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{BS in Finance and Banking \textbar{} Risk Management}
	{Appalachian State University}
	{Boone, NC}
	{2008 – 2012}
	{}
\end{cventries}

\vspace{-4mm}

\cvsection{Projects}
\begin{cventries}
	\cventry
	{Source of truth for accounting system. Listens to pipelines from multiple services, constantly comparing events against state to determine costs / charges associated with various business activity. High traffic, no tolerance for error, constant availability.}
	{Ledger}
	{Scala, Slick, SQL}
	{}
	{}
	
	\vspace{-5mm}
	\cventry
	{System for tracking network test plans, execution history, and the actual execution of those tests on remote devices. REST API and all backend business logic.}
	{CXTM}
	{Python, Flask, SQL, SQLAlchemy, Robot, TextFSM}
	{}
	{}
	
	\vspace{-5mm}
	\cventry
	{Cloud data system for ingesting, sorting, and storing data, using no local resources whatsoever. Querying system for retreiving and using data.}
	{ETL / Data Storage}
	{Python, AWS(S3, Glue, DynamoDB, Lambda, RDS, Athena)}
	{}
	{}
	
\end{cventries}
\end{document}
